Guidelines and Policy for Surveys using \SW

### 2014-05-14 doc/sw-publication-policy-cfhtls.tex
Mostly spelling and grammar, some comments for AV

\begin{itemize}
\item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
\item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
\item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
\item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
\item \sw X: New lenses(s) in \sw (authored by collaboration members)
\end{itemize}

There maybe further series papers (TBC).\newline

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series
\begin{itemize}
\item Lens modelling in \sw (Spaghetti Lens)
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any ideas for further \sw series papers (this includes any publications that include a new lens system that was found by \sw). The authorship policy is defined in the next section.

@@

\subsection{Journal Papers}
\label{sec:series}
A core team of collaborators will participate in writing journal papers, and many collaborators who have made a \textit{significant contribution} to \sw will be recognised on the author
lists of journal papers presenting \sw results.  However, not all collaboration members will participate in writing journal papers.  \textit{Significant contributions} include those who have contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I).

\noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.

The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.

The first author of any \sw paper will decide, as usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting scientists from outside the list of \sw authors, or from outside the
collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.

Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.

@@

\appendix
\section{Current Author List for \sw series papers: author.tex}
\label{sec:appa}
{\small \verbatiminput{authors.tex}}

>>>>

\begin{itemize}
% Old versions of this list, which caused a conflict when I (PJM) merged in
% Aprajita's May 2014 edits. Both look out of date to me! Suggested new 
% version is beneath these.
% 
% <<<<<<< HEAD
% \item \sw I: The system paper, describing the project, the interface, the classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  first results including simulations and community performance (not selection function), means by which you can compute a selection function for any given analysis, list of candidates. 
% \item \sw III: Detailed results on candidates from CFHT-LS \textit{including models, follow-up etc}
% \item \sw IV: Detailed comparison and analysis of citizen scientist classification versus lens-finding
% \item \sw X: New lenses(s) in \sw (authored by collaboration members)
%
% =======
% \item \sw I: The system paper, describing the project, the interface, the
% classification analysis methods (SWAP) and results 
% \item \sw II: The \sw  simulations and community performance (not selection
% function), means by which you can compute a selection function for any given
% analysis. 
% \item \sw III: The first new candidates from CFHT-LS \textit{including models,
% follow-up if feasible}
% \item \sw IV: The results from CFHT-LS search including the comparison and
% analysis of citizen scientist classification versus lens-finding algorithms
% (maybe split into smaller papers).
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8
%
\item \sw I: The system paper, describing the project, the interface, the
classification analysis methods (SWAP) and results from classification of the training set. 
\item \sw II: Results from the CFHTLS project, including new lens candidates, and analysis of \sw compared to previous semi-automatic lens searches in this survey.

There maybe further papers written in this series. \newline

\subsection{\sw Related Papers}
These are \sw related papers but do not necessarily fall into the \sw paper series. Planned examples are:
\begin{itemize}
\item Lens modelling in \sw with {\sc Spaghetti Lens})
\item New lenses(s) in \sw (authored by persons not part of the \sw collaboration)
\end{itemize}

% PJM: not sure if this section should be here, it was part of a conflict I 
% got when I merged... Aprajita?
Please email the \sw PIs at spacewarpspi@googlegroups.com if you have any
ideas for further \sw series papers (this includes any publications that
include a new lens system that was found by \sw). The authorship policy is
defined in the next section.

@@

\subsection{Journal Papers}
\label{sec:series}

A core team of collaborators will participate in writing journal papers, and
many collaborators who have made a \textit{significant contribution} to \sw
will be recognised on the author lists of journal papers presenting \sw
results.  However, not all collaboration members will participate in writing
journal papers.  \textit{Significant contributions} include those who have
contributed to:
\begin{itemize}
\item the site design, construction and operation
\item data preparation or analysis
\item writing and editing the papers. 
\end{itemize}

% PJM: significant conflict here: I think Aprajita's version is the lower one, so that's uncommented for now. Aprajita, can you delete everything that should not be there please? Thanks!

% <<<<<<< HEAD
% The current list of \sw authors is given in the \texttt{authors.tex} file and is reprinted
% in the appendix to this document (see Appendix \ref{sec:appa}); this file shown is as it is currently configured, ready to be copied and pasted into the \sw system paper (\sw I). 
% 
% \noindent The author categories are grouped according to collaboration membership (defined above). These authors have either the status to ``opt-out'' or "opt-in" on \sw publications.  \\
% ``Opt-out'' means the listed people are authors by default on \sw series papers and must explicitly state if they wish for their names to be removed from \sw publications. \\
% ``Opt-in'' means the people listed should be invited to comment on and contribute to publications however it is the decision of the lead author whether to add their names.
% 
% The Principal Investigators, Zooniverse development team and \sw Science team all have ``opt-out'' status and the \sw Affiliates have ``opt-in'' status.
% 
% The first author of any \sw paper will decide, as usual, on the author list of their own paper. This will include adding Affiliates who they think have made a substantial contribution to that investigation, as well as inviting scientists from outside the list of \sw authors, or from outside the
% collaboration.  The \sw PIs will act as adjudicators if any disputes arise, but to be honest we are not expecting any.
% 
% Lead authors of \sw papers should circulate drafts to the list of \sw authors (according to the policy above) and allow a minimum of two weeks to give time for comments. If  ``opt-in'' authors have not provided comments within this time frame they will *not* be included as authors on the paper. If ``opt-out'' authors have not responded to ask for their names to be removed they will be kept on the author list.
% 
% =======
The current list of \sw authors is given in the \texttt{authors.tex} file and
is reprinted in the appendix to this document (see Appendix \ref{sec:appa});
this file shown is as it is currently configured, ready to be copied and
pasted into the \sw system paper (\sw I).

\noindent The author categories are grouped according to collaboration
membership (defined above). These groups of authors have either  ``opt-out''
or ``on contribution'' status regarding \sw publications.  ``Opt-out'' means
the listed people are authors by default and must explicitly state if they
wish for their names to be removed from \sw publications. ``On contribution''
indicates people who will be invited to comment on and contribute to
publications, ``opting in'' to those papers' author lists. The Principal
Investigators, Zooniverse development team and \sw Science team all have
opt-out status and the \sw Affiliates have on contribution status.

The first author of any \sw paper will decide, as usual, on the author list of
their own paper. This will include adding Affiliates who they think have made
a substantial contribution to that investigation, as well as inviting
scientists from outside the list of \sw authors, or from outside the
collaboration.  The PIs will act as adjudicators if any disputes arise, but to
be honest we are not expecting any.

Lead authors of \sw papers should circulate drafts to the list of \sw authors
(according to the policy above) and allow a minimum of two weeks to give time
for comments and to opt-in. If  ``on contribution'' authors have not provided
comments within this time frame they will not be included as authors on the
paper. If ``opt-out'' authors have not responded to ask for their names to be
removed they will be kept on the author list.
% >>>>>>> 34d2fe73486cc68b301665b1b811cff7804137e8

@@

\appendix
\section{Current Author List for \sw series papers:}
\label{sec:appa}
{\small \verbatiminput{authors_core.tex}}

### 2014-05-14 doc/sw-publication-policy-gen.tex
Mostly spelling and grammar, some comments for AV

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  \sw comprises a primary classification interface (www.spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses. In addition, the citizens are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the Citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).

A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).

@@

The \sw collaboration comprises the \sw science team, development team and all the volunteers who have 
logged in\footnote{with a Zooniverse ID. It is possible to classify anonymously, and we count those classification but as we don't know who they are, we are unable to collaborate with them directly.} and contributed classifications to the project.

@@

The \sw PIs will then arrange a hangout/telecon with the SSTs to discuss their project further.

The original \sw papers by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and cite them as justification for some of their decisions. As the \sw paper series get published, links to the papers will be given in this draft. Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})

>>>>

The \sw website is designed to motivate and  enable tens of thousands of
people to perform the scientific tasks of strong gravitational lens
identification and classification.  \sw comprises a primary classification interface (http://spacewarps.org) that allows citizen scientists to inspect images and mark those that contain potential gravitational lenses. In addition, these volunteers are shown simulated lenses (appropriate for the survey being conducted) as an interactive training tool that also allows us to establish the citizens' likelihood of identifying potential lenses and blank fields using the \sw Analysis Pipeline (SWAP).

A key part of the \sw project is the ability for all members of the \sw collaboration (see Section \ref{sec:members}) to communicate with each other and discuss interesting candidates through \Talk\footnote{\Talk (found at \texttt{http://talk.spacewarps.org}) is a forum for \sw collaborators to discuss individual sources and the \sw project in general. Bugs can also be reported. This is the direct portal for communication with the \sw community.}).

@@

The \sw collaboration comprises the \sw science team, \sw development team, and all the volunteers who have 
logged in\footnote{with a Zooniverse ID. It is possible to classify anonymously, and we count those classification but as we don't know who they are, we are unable to collaborate with them directly.} and contributed classifications to the project.

@@

The \sw PIs will then arrange a telecon with the SSTs to discuss their project further.

The original \sw papers, by definition, provide a complete description of the system, and its results from the CFHTLS survey. The science team of
any other survey (such as DES, RCS, KIDS, PS1, HSC \etc) should be able
to read these papers before designing their own \sw project, and cite them as justification for some of their decisions. As the \sw paper series get published, links to the papers will be given in this draft. Prior to publications, draft papers can also be shared on request by the \sw PIs (\href{mailto:spacewarpspi@googlegroups.com}{spacewarpspi@googlegroups.com})
